---
title: "Business Intelligence Lab Submission Markdown"
author: "<135230>"
date: "<22/09/2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                                   |                                                                                            |
|---------------------------------------------------|--------------------------------------------------------------------------------------------|
| **Student ID Numbers and Names of Group Members** |  \<135230 Peter Aringo\>                                                                   |
|                                                   |  \<135356 Ann Kigera\>                                                                     |
|                                                   |  \<122883 Michelle Guya\>                                                                  |
|                                                   |  \<134834 Kasio Emmanuel\>                                                                 |
|                                                   |  \<136301 Ian Nyameta\>                                                                    |
| **BBIT 4.2 Group**                                |       \<Group B\>                                                                          |
| **Course Code**                                   | BBT4206                                                                                    |
| **Course Name**                                   | Business Intelligence II                                                                   |
| **Program**                                       | Bachelor of Business Information Technology                                                |
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                 |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,                        collapse = FALSE, tidy = TRUE)`.

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

# \<Exploratory Data Analysis on Student Performance\>

Describe the code chunk here:

```{r Your Second Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
```

Describe the next code chunk here:

```{r Your Third Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

## \<You Can Have a Sub-Title Here\>

```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

**etc.** as per the lab submission requirements.
