---
title: "Business Intelligence Lab Submission Markdown"
author: "<135230>"
date: "<22/09/2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                                   |                                                                                            |
|---------------------------------------------------|--------------------------------------------------------------------------------------------|
| **Student ID Numbers and Names of Group Members** |  \<135230 Peter Aringo\>                                                                   |
|                                                   |  \<135356 Ann Kigera\>                                                                     |
|                                                   |  \<122883 Michelle Guya\>                                                                  |
|                                                   |  \<134834 Kasio Emmanuel\>                                                                 |
|                                                   |  \<136301 Ian Nyameta\>                                                                    |
| **BBIT 4.2 Group**                                |       \<Group B\>                                                                          |
| **Course Code**                                   | BBT4206                                                                                    |
| **Course Name**                                   | Business Intelligence II                                                                   |
| **Program**                                       | Bachelor of Business Information Technology                                                |
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                 |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,                        collapse = FALSE, tidy = TRUE)`.

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

# \<Exploratory Data Analysis on Student Performance\>

This code first lists the files and directories within the library paths used by R, 
and then it restores the R environment of a project using renv::restore().
```{r Your Second Code Chunk}
library(readr)
.libPaths()
lapply(.libPaths(), list.files)
renv::restore()
```

This code snippet loads the readr library, reads a CSV file, and then
opens an interactive viewer to facilitate the exploration and analysis
of the loaded CSV data.
```{r Your Third Code Chunk}
library(readr)
X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset <- read_csv("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.csv")
View(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset)
```

## \<Analysis of the Data\>
This code calculates the frequency and percentage distribution for three different variables (gender, goal_oriented, and take_quizzes_and_use_results) within the StudentPerformance Dataset.
For each variable, it first assigns the variable to X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq,
then calculates the frequency of unique values using the table function, and finally computes the corresponding 
percentages by dividing the frequencies by the total count and multiplying by 100. The results are stored in two columns, "frequency" and "percentage," and this process is repeated for each of the three variables, allowing one to analyze the distribution of each variable's values in the dataset.
```{r Your Fourth Code Chunk}
X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq <- X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$gender
cbind(frequency = table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq),
      percentage = prop.table(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq)) *100)

X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq <- X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$goal_oriented
cbind(frequency = table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq),
      percentage = prop.table(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq)) *100)

X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq <- X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$take_quizzes_and_use_results
cbind(frequency = table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq),
      percentage = prop.table(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_freq)) *100)
library(readr)
```

 This code snippet calculates the mode for each of the specified variables within the dataset and then prints the mode values. 
 The mode represents the most common value for each variable in the dataset.
```{r Your Fourth Code Chunk}
X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_gender_mode <- names(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$gender))[ # nolint
  which(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$gender) == max(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$gender)))
]
print(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_gender_mode)

X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_goal_oriented_mode <- names(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$goal_oriented))[
  which(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$goal_oriented) == max(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$goal_oriented)))]
print(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_goal_oriented_mode)

X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_take_quizzes_and_use_results_mode <- names(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$take_quizzes_and_use_results))[
  which(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$take_quizzes_and_use_results) == max(table(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset$take_quizzes_and_use_results)))]

print(X20230412_20230719_BI1_BBIT4_1_StudentPerformanceDataset_take_quizzes_and_use_results_mode)
library(readr)
```

```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```


```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```



```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```



```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```



```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```
**etc.** as per the lab submission requirements.
